%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\usepackage{enumitem}
\renewenvironment{entrylist}{%
  \begin{itemize}[leftmargin=1in]%[leftmargin=*,align=left,itemindent=-\dimexpr\labelwidth+\labelindent+\labelsep\relax]
}{%
  \end{itemize}
}
\renewcommand{\bfseries}{\headingfont\color{headercolor}}
\renewcommand{\entry}[4]{%
  \item[#1]
    \textbf{#2}%
    \hfill%
    {\footnotesize\addfontfeature{Color=lightgray} #3}\\%
    #4\vspace{\parsep}%
  }

\begin{document}
\header{Fiona}{ Papiez}
       {Professional Carer}
       {}


% In the aside, each new line forces a line break  
\begin{aside}
  \section{Contact}
    74 Hebron Road
    Stokesley
    North Yorkshire
    TS9 5DF
    ~
    \href{mailto:Fiona.papiez@live.com}{Fiona.papiez@live.com}
    ~
    Tel:(01642) 984542
    Mob:07910119707
    ~
  \section{Key Skills}
   \begin{itemize}
   \item 2+ years in care work
   \item NVQII Qualified (Adult Health and Social Care)
   \item Fast,accurate \\ typist (50wpm+)
   \item Experienced user of Microsoft Office packages
   \item Ability to maintain confidentiality
   \item Excellent spelling and grammar
   \item Ability to work to a deadline/ \\ under pressure
   \end{itemize}
   ~
   ~
   \textbf{Full U.K. Driving licence}
   ~
   \textbf{References available on request}
\end{aside}

\section{Personal Statement}

I began working as a carer in May 2014. I was completely new to this type of work but I found it very fulfilling. Since becoming a care worker I have learned much about the importance of dignity and compassion when helping vulnerable people. I thoroughly enjoy my job and the opportunity it gives me to be part of a close knit group working to benefit the local community.  In February 2015 I was appointed to the position of Medication Senior for the Stokesley area, reflecting my increasing experience and confidence in my role.I have acted as the out of hours contact at Comfort Call for the North Yorkshire area. In this role I was responsible for managing employee schedules to ensure out of hours coverage and deal with unforeseen circumstances.   

In the past I have held a variety of administration/secretarial roles from my recent work at Tata Global Beverages and Univar, to my 13 years at Teesside University and my first job at the Probation Service. The skills I developed range from data-entry, scanning, general correspondence and transcription; to administrative duties such as arranging meetings, travel and conferences, diary management, minute-production, maintenance of staff records and ordering of stationery.In all of these positions I have been required to work with confidential information in both electronic and paper formats. I have excellent verbal and written communication skills, am a fast and accurate typist and have experience with the Microsoft Office suite.

\section{Employment}

\begin{entrylist}
  \entry
    { 05/2014 - present}
    {Carer}
    {Comfort Call Ltd}
    {\emph{My clients range from those with profound disabilities through illness, such as MS, to those who simply need the reassurance of a daily call. In February 2015 I was made Medication Senior for the Stokesley area.\\
    In July 2016 I was made a senior carer for North Yorkshire.}}
  \entry
    {10/2013 - 04/2014}
    {Data-Entry/Q.A. Assistant}
    {Tata Global Beverages, Eaglescliffe}
    {\emph{Selecting samples from production lines, preparing tissue samples, conducting various quality tests, recording data in Microsoft Excel.}}
  \entry
    {12/2012 - 10/2013}
    {Production operative / Packer}
    {Quorn Foods, Stokesley}
    {\emph{Working as part of a team on the Production Line. Duties include packing, palletising,  'spotting', cleaning, some work in 'high-care' production areas.}}
  \entry
    {11/2012 - 12/2012}
    {Temporary Administrative Assistant}
    {Univar Europe, Middlesbrough}
    {\emph{General administrative/clerical duties including typing, filing,\\ scanning/photocopying/faxing, emailing, answering the telephone, data-entry (Microsoft Office, Excel, Outlook, Word).  The company were in the process of migrating to new office management software and I was involved in the scanning, uploading and data-entry of mass documents into SAP.}}
  \entry
    {1996-2004}
    {Personal Assistant to my ex-husband}
    {Freelance IT consultancy}
    {\emph{Typing, filing, answering the telephone, making travel arrangements, preparing invoices etc.}}
    \entry
    {07/1980 - 04/1991}
    {Deparmental Assistant}
    {Teesside University; Computer Centre}
    {\emph{Provision of clerical and secretarial support to senior staff, production/typing of minutes and correspondence (from dictation or audio), technical documents, PhD theses etc.  Conference organisation, reception duties including setting-up student and staff accounts on the computer systems.  Ordering stationery, recording holidays and sickness, organising travel and accommodation for Centre staff.}}
    \end{entrylist}
    \begin{entrylist}
    \entry
    {11/1978 - 07-1980}
    {Shorthand/Typist}
    {Teesside University; Central Administration}
    {\emph{As a member of the Typing Pool, providing a typing service to Administrative and other university staff.  This job also involved being seconded to academic departments to provide secretarial support.}}
    \entry
    {08/1978 - 11/1978}
    {Shorthand/Typist/Clerk}
    {Cleveland Probation Service; Headquarters}
    {\emph{Providing secretarial support to the Administrative Officer.}}
\end{entrylist}



\section{Education}

\begin{entrylist}
  \entry
    {2016}
    {Working towards NVQIII Health \& Social Care (Adult)}
    {Lifetime Learning}
    {}
  \entry
    {2015}
    {NVQ II Health \& Social Care (Adult)}
    {Lifetime Learning}
    {}
  \entry
    {09/2012 - 10/2012}
    {Edexcel BTEC Level 2 Certificate in Supporting Employability and Personal Effectiveness.}
    {Talent Training}
    {}
  \entry
    {1996-1999}
    {Diploma in Music}
    {The Open University}
    {\emph{Modules Studied: A102 Arts Foundation Course, A214 Understanding Music, AA302 From Composition to Performance. }}
  \entry
    {1977-1978}
    {LCCI Secretarial Studies Certificate}
    {Kirby College of Further Education}
    {\emph{Components included Typing, Shorthand, Audio-Typing, Office Practice, English, Business Studies;
    RSA Typing II, RSA English; Pitman Shorthand, various speeds up to 120wpm, Pitman Typing/Audio Typing}}
  \entry
    {1975-1977}
    {GCE O-Levels}
    {Stokesley School}
    {\emph{English Language C, English Literature C, History C, CSE French 2, German 2, Art \& Design, Typing.}}
  \end{entrylist}

\section{Voluntary Work}

\begin{entrylist}
  \entry
    {2004}
    {Shop Assistant}
    {Help the Aged, Stokesley}
    {}
  \entry
    {01/1985 - 07/1986}
    {Sub-Warden}
    {Teesside University (Polytechnic); Middleton-St-George Halls of Residence}
    {\emph{This residential post involved assisting students with any problems regarding their accommodation, arranging for repairs and maintenance with the senior warden, inspecting rooms and booking in/out students at the start and end of term, carrying out fire-drills.}}
 \end{entrylist}



\end{document}
